NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-02-22 Manuscript/manuscriptPS.tex
Updates in the manuscript and density plot
Add new dihedrals to manuscript

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/comparisonTablePS.pdf}
  \caption{\label{comparisonTablePS}
  Rough subjective ranking of force fields based on Figure~\ref{HGorderParametersPS}. Here ÒMÓ indicates a magnitude problem, ÒFÓ a forking problem; letter size increases with problem severity. Color scheme: Òwithin experimental errorÓ (dark green), Òalmost within experimental errorÓ (light green), Òclear deviation from experimentsÓ (light red), and Òmajor deviation from experimentsÓ (dark red). The $\Sigma$-column shows the total deviation of the force field, when individual carbons are given weights of 0 (matches experiment), 1, 2, and 4 (major deviation). For full details of the assessment, see Supplementary Information.
  }
\end{figure}

The headgroup order parameters of DOPS and POPS bilayers 
from different simulation models are compared with the experimental
data in Fig. \ref{HGorderParametersPS}. In line with the previous
study for PC lipids \cite{botan15}, the glycerol backbone order 
parameters in CHARMM36 and Berger force fields roughly agree with
the experimental data, but significant discrepancies are observed for
Slipids and CKP models. The glycerol backbone structures from CHARMM36 and
Slipids simulations visualized in Fig. \ref{glycerol_buslaev} reveal the
missing structures in Slipids model, which probably lead to the incorrect
order parameters. For the headgroup $\alpha$ and $\beta$ carbon order parameters of PS lipids,
the tested models perform less well than for PC headgroup in previous
study \cite{botan15}. None of the tested models give a satisfactory 
agreement with experiments for the headgroup order paramaters of 
PS lipids. Based on the subjective ranking shown in Fig. \ref{comparisonTablePS},
the CHARMM36 is the best performing model for both lipids.
However, the total deviation from the experiments for the PS lipids is significantly
higher for PS lipids (8) than for PC (3) \cite{botan15}. Therefore the 
interpretation of structural differences between PC and PS lipids 
from current MD simulation models is very challenging.

@@

\section{Dihedrals}
\begin{figure*}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/dihed1.png}
  \includegraphics[width=8.0cm]{../Figs/dihed2.png}
  \includegraphics[width=8.0cm]{../Figs/dihed3.png}
  \includegraphics[width=8.0cm]{../Figs/dihed4.png}
  \includegraphics[width=8.0cm]{../Figs/dihed5.png}
  \includegraphics[width=8.0cm]{../Figs/dihed6.png}
  \includegraphics[width=8.0cm]{../Figs/dihed7.png}
  \includegraphics[width=8.0cm]{../Figs/dihed8.png}
  \includegraphics[width=8.0cm]{../Figs/dihed9.png}
  \includegraphics[width=8.0cm]{../Figs/dihed10.png}
  \caption{\label{dihedrals}
    Experimental results for sign measurement for POPS sample
  }
\end{figure*}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/comparisonTablePS.pdf}
  \caption{\label{comparisonTablePS}
  Rough subjective ranking of force fields based on Figure~\ref{HGorderParametersPS}. Here ÒMÓ indicates a magnitude problem, ÒFÓ a forking problem; letter size increases with problem severity. Color scheme: Òwithin experimental errorÓ (dark green), Òalmost within experimental errorÓ (light green), Òclear deviation from experimentsÓ (light red), and Òmajor deviation from experimentsÓ (dark red). The $\Sigma$-column shows the total deviation of the force field, when individual carbons are given weights of 0 (matches experiment), 1, 2, and 4 (major deviation). For full details of the assessment, see Supplementary Information.
  }
  \todo{Issue about possible updates to this plot: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/4}
\end{figure}

The headgroup order parameters of DOPS and POPS bilayers 
from different simulation models are compared with the experimental
data in Fig. \ref{HGorderParametersPS}. In line with the previous
study for PC lipids \cite{botan15}, the glycerol backbone order 
parameters in CHARMM36 roughly agree with the experimental data,
while significant discrepancies are observed in other models at
least for one glycerol backbone carbons.
\todo{Discussion to be finished once all the results are in the plot.}

The glycerol backbone structures from CHARMM36 and
Slipids simulations visualized in Fig. \ref{glycerol_buslaev} reveal the
missing structures in Slipids model, which probably lead to the incorrect
order parameters. For the headgroup $\alpha$ and $\beta$ carbon order parameters of PS lipids,
the tested models perform less well than for PC headgroup in previous
study \cite{botan15}. None of the tested models give a satisfactory 
agreement with experiments for the headgroup order paramaters of 
PS lipids. Based on the subjective ranking shown in Fig. \ref{comparisonTablePS},
the CHARMM36 is the best performing model for both lipids.
However, the total deviation from the experiments for the PS lipids is significantly
higher for PS lipids (8) than for PC (3) \cite{botan15}. Therefore the 
interpretation of structural differences between PC and PS lipids 
from current MD simulation models is very challenging.

@@

\section{Dihedrals}
\begin{figure*}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/diheds_pops1.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops2.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops3.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops4.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops5.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops6.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops7.png}
  \caption{\label{dihedralsGLY}
    Dihedral angle distributions of bonds from phosphate to acyl chain carbonyls from different simulation models.
  }
\end{figure*}
\section{Dihedrals}
\begin{figure*}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/diheds_pops8.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops9.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops10.png}
  \includegraphics[width=8.0cm]{../Figs/diheds_pops11.png}
  \caption{\label{dihedralsHG}
    Dihedral angle distributions of bonds from phosphate to headgroup from different simulation models.
  }
\end{figure*}
